---
name: "Main Report-new"
author: "HIV Estimates Accuracy tool"
title: "Multiple imputations"
date: "`r format(Sys.time(), '%d %B %Y, %H:%M:%S')`"
output:
  html_fragment:
    smart: yes
    toc: yes
    number_sections: yes
  html_document:
    highlight: null
    mathjax: null
    number_sections: yes
    self_contained: yes
    theme: default
    toc: yes
    toc_float:
      collapsed: false
      smooth_scroll: false
  latex_document:
    toc: yes
    template: default
    highlight: null
    citation_package: none
  pdf_document:
    toc: yes
    template: default
    highlight: null
    citation_package: none
  word_document:
    reference_docx: ./resources/template_ECDC.docx
    fig_width: 7
    fig_height: 4
    toc: yes
params:
  AdjustedData: NA
  ReportingDelay:
    label: "Adjust count of cases for reporting delay"
    value: TRUE
    input: checkbox
  Smoothing:
    label: "Apply plot curves smoothing"
    value: FALSE
    input: checkbox
  CD4ConfInt:
    label: "Plot confidence intervals in CD4 count plots"
    value: FALSE
    input: checkbox
editor_options: 
  chunk_output_type: console
---

```{r setup, eval = TRUE, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      results = "asis", 
                      message = FALSE, 
                      warning = FALSE, 
                      include = TRUE, 
                      fig.height = 4,
                      fig.width = 10,
                      dev = "svg")
```

```{r, eval = TRUE, include = FALSE}
# Setup ------------------------------------------------------------------------
require(data.table)
require(ggplot2)
require(mitools)
require(quantreg)

colorPalette <- c("#69b023", "#7bbcc0", "#9d8b56", "#ce80ce", "#b23A48", "#7a5980", "#63372c", "#284b63")
colNamesMapping <- 
  c(DateOfDiagnosisYear = "Year of diagnosis",
    Total = "Total",
    Overall = "Overall",
    F = "Female",
    M = "Male",
    O = "Other",
    HAEMO = "Haemophilia",
    HETERO = "Hetero",
    IDU = "IDU",
    MTCT = "MTCT",
    MSM = "MSM",
    NOSO = "Nosocomial",
    TRANSFU = "Transfusion",
    Missing = "Missing")
colNamesMappingTable <- 
  setNames(
    c(colNamesMapping[1],
    paste(colNamesMapping[2], "[N]"),
    paste(colNamesMapping[-c(1:2)], "[N (%)]")),
    names(colNamesMapping))

# Functions --------------------------------------------------------------------

FormatNumbers <- function(
  x,
  digits = 0
) {
  selNA <- is.na(x)
  res <- rep("-", length(x))
  res[!selNA] <- sprintf(paste0("%.", digits, "f"), x[!selNA])

  return(res)
}

FormatRangeCols <- function(
  data,
  digits = 0
) {
  if (ncol(data) == 2) {
    res <- paste0(FormatNumbers(data[[1]], digits), " (",
                  FormatNumbers(data[[2]], digits), ")")
  } else {
    res <- paste0(FormatNumbers(data[[2]], digits), " (",
                  FormatNumbers(data[[1]], digits), ", ",
                  FormatNumbers(data[[3]], digits),")")
  }

  return(res)
}

GetAggregatedData <- function(
  data,
  rowvar,
  colvar,
  aggrExpr = ".(Count = .N)"
) {
  expr <- parse(text = aggrExpr)

  aggr1 <- data[, {eval(expr, envir = data)}, by = c(rowvar, colvar)]
  aggr2 <- data[, {eval(expr, envir = data)}, by = c(rowvar)]
  aggr3 <- data[, {eval(expr, envir = data)}, by = c(colvar)]
  aggr4 <- data[, {eval(expr, envir = data)}]

  aggr2[, (colvar) := "Overall"]
  aggr3[, (rowvar) := "Total"]
  aggr4[, c(rowvar, colvar) := .("Total", "Overall")]

  dt <- rbindlist(list(aggr1, aggr2, aggr3, aggr4),
                  use.names = TRUE)

  allComb <- CJ(rowvar = unique(dt[[rowvar]]),
                colvar = unique(dt[[colvar]]))
  setnames(allComb,
           old = c("rowvar", "colvar"),
           new = c(rowvar, colvar))

  dt <- dt[allComb, on = c(rowvar, colvar)]

  if ("Count_Val" %in% colnames(dt)) {
    dt[,
       Count_Perc := Count_Val / sum(Count_Val, na.rm = TRUE) * 100,
       by = c(rowvar)]
  }

  return(dt)
}

GetReportTable <- function(
  data,
  rowvar,
  colvar,
  vvars,
  mapping = colNamesMappingTable,
  digits = 0
) {
  if (is.null(data)) {
    return(NULL)
  }
  
  dt <- dcast(data,
              as.formula(sprintf("%s ~ %s", rowvar, colvar)),
              value.var = vvars)

  colLevels <- levels(data[[colvar]])
  for (val in colLevels) {
    valColNames <- grep(paste0("_", val, "$"),
                        paste(vvars, val, sep = "_"),
                        value = TRUE)
    dt[, (val) := FormatRangeCols(.SD, digits = digits), .SDcols = valColNames]
  }
  dt <- dt[, c(rowvar, colLevels), with = FALSE]
  if (!is.null(mapping)) {
    mapping <- mapping[names(mapping) %in% colnames(dt)]
    setnames(dt,
             old = names(mapping),
             new = mapping)
  }

  dt <- knitr::kable(dt, 
                     align = rep("r", ncol(dt)))

  return(dt)
}

GetReportPlot <- function(
  data,
  rowvar,
  colvar,
  vvars,
  cd4YLim = NULL,
  probsStr = NULL,
  confIntervals = FALSE,
  mapping = colNamesMapping,
  colors = colorPalette
) {
  if (is.null(data)) {
    return(NULL)
  }

  plotObj <- ggplot(data = data,
                    aes(x = as.integer(get(rowvar)),
                        y = get(vvars[1]),
                        color = get(colvar),
                        fill = get(colvar))) +
    geom_line(size = 0.5) +
    geom_point(size = 1.5) +
    scale_x_continuous(expand = c(0, 0), breaks = data[, as.integer(sort(unique(get(rowvar))))]) +
    scale_y_continuous(expand = c(0, 0)) +
    expand_limits(y = c(0, cd4YLim)) +
    scale_colour_manual(name = colvar,
                        labels = mapping,
                        values = colors) +
    scale_fill_manual(name = colvar,
                      labels = mapping,
                      values = colors) +
    theme_classic() +
    theme(axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8)) +
    labs(x = "Year", 
         y = expression("Median CD4 cell count (cells/"*mu*"L)"))

  if (confIntervals) {
    plotObj <- plotObj +
      geom_ribbon(aes(ymin = get(vvars[2]),
                      ymax = get(vvars[3])),
                  alpha = 0.1,
                  colour = NA)
  }

  return(plotObj)
}

GetModelledQuantileData <- function(
  data,
  rowvar,
  colvar,
  vvar,
  nsdf,
  probs = c(CD4_Low = 0.25, CD4_Median = 0.5, CD4_High = 0.75)
) {
  dataList <- imputationList(split(
    data[, c(vvar, colvar, rowvar, "DY", "Imputation", "ModelWeight"),
         with = FALSE],
    by = "Imputation"))
  result <- NULL
  for (probName in names(probs)) {
    prob <- probs[probName]
    if (optSmoothing) {
      models <-
        with(dataList,
             rq(formula =
                  as.formula(sprintf("%s ~ %s * splines::ns(DY, df = nsdf)",
                                     vvar, colvar)),
                tau = prob,
                data = dataList$imputations,
                weights = ModelWeight,
                method = "br"))
      vars <- MIextract(models, fun = function(model) {
        diag(summary(model, covariance = TRUE)$cov)
      })
    } else {
      models <-
        with(dataList,
             rqss(formula =
                    as.formula(sprintf("%s ~ %s * as.factor(DY)", vvar, colvar)),
                  tau = prob,
                  data = dataList$imputations,
                  weights = ModelWeight,
                  method = "sfn"))
      vars <- MIextract(models, fun = function(model) {
        diag(as.matrix(summary(model, cov = TRUE)$Vcov))
      })
    }

    betas <- MIextract(models, fun = coefficients)
    t <- MIcombine(betas, vars)
    X <- model.matrix(models$`1`$formula)
    linpred <- (X %*% coef(t))^2
    pred <- cbind(dataList$imputations$`1`,
                  Linpred = as.vector(linpred))
    pred <- unique(pred[, c(rowvar, colvar, "Linpred"), with = FALSE])

    if (is.null(result)) {
      result <- copy(pred)
    } else {
      result <- cbind(result, Linpred = pred$Linpred)
    }
    setnames(result, "Linpred", probName)
  }
  return(result)
}

GetModelledCountData <- function(
  data,
  colvar,
  nsdf
) {
  data <- data[,
               .(Count_Val = sum(ModelWeight, na.rm = TRUE)),
               by = c("Imputation", "DateOfDiagnosisYear", colvar)]
  if (nrow(data) > 0) {
    data[, DY := DateOfDiagnosisYear - min(DateOfDiagnosisYear)]
  } else {
    data[, DY := integer()]
  }
  
  # mitools doesn't like factors with 0 frequency levels
  data[, (colvar) := droplevels(get(colvar))]

  # Fit saturated Poisson model to MI data
  dataList <- imputationList(split(data, by = "Imputation"))

  # Main model
  if (optSmoothing) {
    suppressWarnings({
      models <- with(dataList,
                     glm(formula = 
                           as.formula(sprintf("Count_Val ~ as.factor(%s) * splines::ns(DY, df = nsdf)", 
                                              colvar)),
                         data = data,
                         family = poisson(link = log)))
    })
  } else {
    suppressWarnings({
      models <- with(dataList,
                     glm(formula = 
                           as.formula(sprintf("Count_Val ~ as.factor(%s) * as.factor(DY)", 
                                              colvar)),
                         data = data,
                         family = poisson(link = log)))
    })
  }

  # Extract betas and var
  betas <- MIextract(models, fun = coefficients)
  vars <- MIextract(models, fun = vcov)

  # Rubin's rules applied by MIcombine
  t <- MIcombine(results = betas, variances = vars)
  X <- model.matrix(models$`1`$formula)
  X <- X[, names(betas$`1`)]

  # Linear predictor exponentiated to get predicted counts
  if (anyNA(coef(t))) {
    naCoef <- which(is.na(coef(t)))
    linpred <- exp(X[, -naCoef] %*% coef(t)[-naCoef])
  } else{
    linpred <- exp(X %*% coef(t))
  }

  # Manipulation to end-up with a wide-format dataframe
  pred <- cbind(dataList$imputations$`1`,
                Count_Val = as.vector(linpred))
  pred <- pred[, c("DateOfDiagnosisYear", colvar, "Count_Val"), with = FALSE]

  return(pred)
}

GetModelledDataAdaptive <- function(
  colvar,
  colNamesMapping,
  distr,
  modelFunc,
  thresholds = c(0.001, 0.002, 0.005, 0.01, 0.02, 0.05, 0.1),
  ...
) {
  result <- NULL
  message <- NULL
  badCategories <- NULL
  for (threshold in thresholds) {
    badCategories <- distr[Perc < threshold, unique(get(colvar))]
    filteredData <- FilterData(data, colvar, badCategories)

    result <- suppressWarnings({
      try(modelFunc(colvar = colvar, ...), silent = TRUE)
    })
    if (!inherits(result, "try-error")) {
      if (length(badCategories) > 0) {
        message <-
          sprintf("<p>Persons which were %s anywhere (i.e. even in one imputed dataset) are removed. Threshold of %2.2f%% of count per category within the dataset was applied.</p>",
                  paste(colNamesMapping[as.character(badCategories)],
                        collapse = ", "),
                  threshold * 100)
      }
      break
    }
  }
  
  return(list(Result = result,
              Message = message,
              BadCategories = badCategories))
}

FilterData <- function(data, colvar, badCategories)
{
  if (length(badCategories) > 0) {
    badIds <- data[get(colvar) %in% badCategories, unique(id)]
    filteredData <- data[!id %in% badIds]
    filteredData[, (colvar) := droplevels(get(colvar))]
  } else {
    filteredData <- data
  }

  return(filteredData)
}

GetRDReportTable <- function(data) 
{
  if (is.null(data)) {
    return(NULL)
  }
  
  dt <- copy(data)
  numericCols <- setdiff(colnames(dt), c("DateOfDiagnosisYear"))
  dtTotals <- dt[, lapply(.SD, sum, na.rm = TRUE), .SDcols = numericCols]
  dtTotals[, DateOfDiagnosisYear := "Total"]
  ConvertDataTableColumns(dt, c(DateOfDiagnosisYear = "character"))
  dt <- rbind(dt, 
                       dtTotals)
  dt[, (numericCols) := lapply(.SD, FormatNumbers), .SDcols = numericCols]
  setorderv(dt, c("DateOfDiagnosisYear"))
  tableColNames <- c("Diagnosis<br />year", 
                     "Missing<br />details", 
                     "Reported",
                     "Unreported", 
                     "Estimated total", 
                     "Estimated total<br />lower bound", 
                     "Estimated total<br />upper bound")
  dt <- knitr::kable(dt,
                     align = rep("r", ncol(dt)),
                     col.names = tableColNames)

  return(dt)  
}

# Processing -------------------------------------------------------------------

optReportingDelay <- as.logical(params$ReportingDelay)
optSmoothing <- as.logical(params$Smoothing)
optCD4ConfInt <- as.logical(params$CD4ConfInt)

finalDataIdx <- length(params$AdjustedData)
data <- copy(params$AdjustedData[[finalDataIdx]]$Table)

cd4Present <- data[, any(!is.na(SqCD4))]
adjTypes <- sapply(params$AdjustedData, "[[", "Type")
miPresent <- length(adjTypes[adjTypes == "MULTIPLE_IMPUTATIONS"]) > 0
rdPresent <- length(adjTypes[adjTypes == "REPORTING_DELAYS"]) > 0

# Determine last MI adjustment, if any, to get "nsdf" parameter
miAdjName <- tail(names(adjTypes[adjTypes == "MULTIPLE_IMPUTATIONS"]), 1)
if (length(miAdjName) == 1) {
  nsdf <- params$AdjustedData[[miAdjName]]$Parameters$nsdf
} else {
  nsdf <- 5L
}

# Create and initialize requried columns
if (!miPresent) {
  data[, Imputation := 0L]
}

if (rdPresent & optReportingDelay) {
  data[, ModelWeight := Weight]
} else {
  data[, ModelWeight := 1.0]
}

# A. Make manipulations ---
data[Transmission %in% c(NA, "NA", ""), Transmission := "Missing"]

# Original data
dataOrig <- data[Imputation == 0L]
dataOrig[, ':='(
  CD4 = SqCD4^2,
  Transmission = factor(Transmission),
  Gender = factor(Gender)
)]

# MI data
dataMI <- data[Imputation != 0L]
dataMI[, ':='(
  Transmission = factor(Transmission),
  Gender = factor(Gender)
)]

dataMIGenderCountDistr <- 
  dataMI[, .(Count = .N), by = .(Gender)][, Perc := Count / sum(Count)]
dataMITransCountDistr <- 
  dataMI[, .(Count = .N), by = .(Transmission)][, Perc := Count / sum(Count)]

# Unadjusted
dataOrigGender <-
  GetAggregatedData(
    data = dataOrig,
    rowvar = "DateOfDiagnosisYear",
    colvar = "Gender",
    aggrExpr =
      "{
        count <- .N
        quant <- quantile(CD4, na.rm = TRUE, probs = c(0.25, 0.5, 0.75), names = FALSE)
        list(
          Count_Val = count,
          CD4_Low = quant[1],
          CD4_Median = quant[2],
          CD4_High = quant[3])
      }")

dataOrigTrans <-
  GetAggregatedData(
    data = dataOrig,
    rowvar = "DateOfDiagnosisYear",
    colvar = "Transmission",
    aggrExpr =
      "{
        count <- .N
        quant <- quantile(CD4, na.rm = TRUE, probs = c(0.25, 0.5, 0.75), names = FALSE)
        list(
          Count_Val = count,
          CD4_Low = quant[1],
          CD4_Median = quant[2],
          CD4_High = quant[3])
      }")

dataMIGenderCD4 <- NULL
dataMITransCD4 <- NULL
dataMITransCount <- NULL
if (miPresent) {
  if (cd4Present) {
    # Quantile regressions not possible with rare categories and discrete time
    # extrapolated - dodgy results from quantile regressions with rare
    # categories and smoothed time rare categories removed.
    dataMIGenderCD4List <-
      GetModelledDataAdaptive(
        data = dataMI,
        modelFunc = GetModelledQuantileData,
        colvar = "Gender",
        rowvar = "DateOfDiagnosisYear",
        vvar = "SqCD4",
        distr = dataMIGenderCountDistr,
        nsdf = nsdf,
        colNamesMapping = colNamesMappingTable)
    dataMITransCD4List <-
      GetModelledDataAdaptive(
        data = dataMI,
        modelFunc = GetModelledQuantileData,
        colvar = "Transmission",
        rowvar = "DateOfDiagnosisYear",
        vvar = "SqCD4",
        distr = dataMITransCountDistr,
        nsdf = nsdf,
        colNamesMapping = colNamesMappingTable)
    
    dataMIGenderCD4 <- dataMIGenderCD4List[["Result"]]
    dataMITransCD4 <- dataMITransCD4List[["Result"]]
    
    transBadCategories <- dataMITransCD4List[["BadCategories"]]
  } else {
    transBadCategories <- c()
  }

  # Prefilter data on the same categories as in CD4 modelling
  dataMI <- 
    FilterData(
      data = dataMI, 
      colvar = "Transmission",
      badCategories = transBadCategories)
  dataMITransCountList <- 
    GetModelledDataAdaptive(
      data = dataMI,
      modelFunc = GetModelledCountData,
      colvar = "Transmission",                    
      distr = dataMITransCountDistr,
      nsdf = nsdf)
  dataMITransCount <- 
    GetAggregatedData(
      data = dataMITransCountList[["Result"]],
      rowvar = "DateOfDiagnosisYear",
      colvar = "Transmission",
      aggrExpr = ".(Count_Val = sum(Count_Val, na.rm = TRUE))")
}

cd4YLim <- NULL
if (cd4Present) {
  if (miPresent) {
    cd4YLim <- 
      GetNiceUpperLimit(max(
        dataOrigTrans[DateOfDiagnosisYear != "Total", CD4_Median],
        dataOrigTrans[DateOfDiagnosisYear != "Total", CD4_Median],
        dataMIGenderCD4$CD4_Median,
        dataMITransCD4$CD4_Median,
        na.rm = TRUE))
  } else {
    cd4YLim <- 
      GetNiceUpperLimit(max(
        dataOrigTrans[DateOfDiagnosisYear != "Total", CD4_Median],
        dataOrigTrans[DateOfDiagnosisYear != "Total", CD4_Median],
        na.rm = TRUE))
  }
}

rdData <- NULL
if (rdPresent) {
  rdIdx <- tail(grep("^REPORTING_DELAYS$", adjTypes), 1)
  rdData <- params[["AdjustedData"]][[rdIdx]][["Artifacts"]][["ReportTableData"]]
}

# PRODUCE OUTPUTS --------------------------------------------------------------
tblOrigGenderCount <- 
  GetReportTable(data = dataOrigGender,
                 rowvar = "DateOfDiagnosisYear",
                 colvar = "Gender",
                 vvars = c("Count_Val", "Count_Perc"))
plotOrigGenderCount <- 
  GetReportPlot(data = dataOrigGender[DateOfDiagnosisYear != "Total" & Gender != "Overall"],
                rowvar = "DateOfDiagnosisYear",
                colvar = "Gender",
                vvars = "Count_Val")

tblOrigGenderCD4 <- 
  GetReportTable(data = dataOrigGender,
                 rowvar = "DateOfDiagnosisYear",
                 colvar = "Gender",
                 vvars = c("CD4_Low", "CD4_Median", "CD4_High"))
plotOrigGenderCD4 <- 
  GetReportPlot(data = dataOrigGender[DateOfDiagnosisYear != "Total" & Gender != "Overall"],
                rowvar = "DateOfDiagnosisYear",
                colvar = "Gender",
                vvars = c("CD4_Median", "CD4_Low", "CD4_High"),
                confIntervals = TRUE,
                cd4YLim = cd4YLim)
tblMIGenderCD4 <- 
  GetReportTable(data = dataMIGenderCD4,
                 rowvar = "DateOfDiagnosisYear",
                 colvar = "Gender",
                 vvars = c("CD4_Low", "CD4_Median", "CD4_High"))
plotMIGenderCD4 <- 
  GetReportPlot(data = dataMIGenderCD4[DateOfDiagnosisYear != "Total" & Gender != "Overall"],
                rowvar = "DateOfDiagnosisYear",
                colvar = "Gender",
                vvars = c("CD4_Median", "CD4_Low", "CD4_High"),
                confIntervals = TRUE,
                cd4YLim = cd4YLim)

tblOrigTransCount <- 
  GetReportTable(data = dataOrigTrans,
                 rowvar = "DateOfDiagnosisYear",
                 colvar = "Transmission",
                 vvars = c("Count_Val", "Count_Perc"))
plotOrigTransCount <- 
  GetReportPlot(data = dataOrigTrans[DateOfDiagnosisYear != "Total" & Transmission != "Overall"],
                rowvar = "DateOfDiagnosisYear",
                colvar = "Transmission",
                vvars = "Count_Val")
tblMITransCount <- 
  GetReportTable(data = dataMITransCount,
                 rowvar = "DateOfDiagnosisYear",
                 colvar = "Transmission",
                 vvars = c("Count_Val", "Count_Perc"))
plotMITransCount <- 
  GetReportPlot(data = dataMITransCount[DateOfDiagnosisYear != "Total" & Transmission != "Overall"],
                rowvar = "DateOfDiagnosisYear",
                colvar = "Transmission",
                vvars = "Count_Val",
                cd4YLim = cd4YLim)

tblOrigTransCD4 <- 
  GetReportTable(data = dataOrigTrans,
                 rowvar = "DateOfDiagnosisYear",
                 colvar = "Transmission",
                 vvars = c("CD4_Low", "CD4_Median", "CD4_High"))
plotOrigTransCD4 <- 
  GetReportPlot(data = dataOrigTrans[DateOfDiagnosisYear != "Total" & Transmission != "Overall"],
                rowvar = "DateOfDiagnosisYear",
                colvar = "Transmission",
                vvars = c("CD4_Median", "CD4_Low", "CD4_High"),
                confIntervals = TRUE,
                cd4YLim = cd4YLim)
tblMITransCD4 <- 
  GetReportTable(data = dataMITransCD4,
                 rowvar = "DateOfDiagnosisYear",
                 colvar = "Transmission",
                 vvars = c("CD4_Low", "CD4_Median", "CD4_High"))
plotMITransCD4 <- 
  GetReportPlot(data = dataMITransCD4[DateOfDiagnosisYear != "Total" & Transmission != "Overall"],
                rowvar = "DateOfDiagnosisYear",
                colvar = "Transmission",
                vvars = c("CD4_Median", "CD4_Low", "CD4_High"),
                confIntervals = TRUE,
                cd4YLim = cd4YLim)

tblRd <- GetRDReportTable(data = rdData)
```

--------------------------------------------------------------------------------

# Introduction

```{r}
cat("<p>Adjustments:</p>") 
cat("<ol>")
cat(sprintf("<li>%s</li>",
            ifelse(miPresent,
                   "Multiple Imputations adjustment performed.",
                   "Multiple Imputations adjustment not performed.")))
cat(sprintf("<li>%s</li>",
            ifelse(rdPresent,
                   "Reporting Delays adjustment performed.",
                   "Reporting Delays adjustment not performed.")))
cat("</ol>")

cat("<p>Selected report options:</p>") 
cat("<ol>")
cat(sprintf("<li>%s</li>", 
            ifelse(optReportingDelay, 
                   "Correction of count of cases for reporting delay.",
                   "Original count of case.")))
cat(sprintf("<li>%s</li>", 
            ifelse(optSmoothing, 
                   "Smoothed version of calendar time.",
                   "Original calendar time.")))
cat(sprintf("<li>%s</li>", 
            ifelse(optCD4ConfInt, 
                   "CD4 plots with confidence interval.",
                   "CD4 plots without confidence interval.")))
cat("</ol>")

if (!cd4Present) {
  cat("<p>CD4 count is missing in both the unadjusted and the adjusted data. All CD4 related tables and figures are omitted in this report.</p>")  
}
```

--------------------------------------------------------------------------------

# Comparison of data by Gender

## Number of diagnoses per year

Data stratified by *gender* is shown only for unadjusted data since there were 
no missing data on *gender* after pre-processing, which takes place before 
adjustments.

### Before and after adjustments

```{r}
plotOrigGenderCount
tblOrigGenderCount
```

## Median CD4 cell count (cells/$\mu$L)

```{r, eval = cd4Present}
cat("### Before adjustments", "\n")
plotOrigGenderCD4
tblOrigGenderCD4
```

```{r, eval = cd4Present & miPresent}
cat("### After adjustments", " \n")
plotMIGenderCD4
tblMIGenderCD4
if (!IsEmptyString(dataMIGenderCD4List[["Message"]])) {
  cat(dataMIGenderCD4List[["Message"]], "\n")
}
```

```{r, eval = cd4Present & !miPresent}
cat("CD4 cell count after adjustments is not available since no imputation adjustements have been run.", "\n")
```

```{r, eval = !cd4Present}
cat("CD4 cell count results are not available due to full missingness of this attribute in the input data.", "\n")
```

--------------------------------------------------------------------------------

# Comparison of data by Transmission

## Number of diagnoses per year

### Before adjustments

```{r}
plotOrigTransCount
tblOrigTransCount
```

```{r, eval = miPresent}
cat("### After adjustments", "\n")
plotMITransCount
tblMITransCount
if (!IsEmptyString(dataMITransCountList[["Message"]])) {
  cat(dataMITransCountList[["Message"]], "\n")
}
```

## Median CD4 cell count (cells/$\mu$L)

```{r, eval = cd4Present}
cat("### Before adjustments", "\n")
plotOrigTransCD4
tblOrigTransCD4
```

```{r, eval = cd4Present & miPresent}
cat("### After adjustments", "\n")
plotMITransCD4
tblMITransCD4
if (!IsEmptyString(dataMITransCD4List[["Message"]])) {
  cat(dataMITransCD4List[["Message"]], "\n")
}
```

```{r, eval = cd4Present & !miPresent}
cat("CD4 cell count after adjustments is not available since no imputation adjustements have been run.", "\n")
```

```{r, eval = !cd4Present}
cat("CD4 cell count results are not available due to full missingness of this attribute in the input data.", "\n")
```

```{r, eval = rdPresent}
cat("-------------------------------------------------------------------", "\n")
cat("\n")
cat("# Comparison of the reported and estimated number of diagnoses per year", "\n")
tblRd

```
