---
name: "Multiple Imputations"
author: "HIV Estimates Accuracy tool"
title: "Multiple imputations"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_fragment:
    number_sections: yes
    smart: yes
  html_document:
    highlight: null
    mathjax: null
    number_sections: yes
    self_contained: yes
    theme: default
    toc: yes
    toc_float: no
  pdf_document:
    toc: yes
    template: default
    highlight: null
  word_document:
    reference_docx: ./resources/template_ECDC.docx
    fig_width: 7
    fig_height: 4
    toc: yes
params:
  AdjustedData: NA
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "asis", message = FALSE, warning = FALSE, include = TRUE, fig.height = 4)
```

```{r include = FALSE}
require(data.table)
require(ggplot2)
require(mitools)
require(quantreg)

# C. Functions definitions ---

# Returns Median (IQR) as string
mediqr <- function(v, digits = 0) {
  med <- quantile(v, na.rm = TRUE, probs = 0.5)
  q1  <- quantile(v, na.rm = TRUE, probs = 0.25)
  q3  <- quantile(v, na.rm = TRUE, probs = 0.75)
  res <- paste0(round(med, digits)," (",round(q1, digits),", ",round(q3, digits),")")
  return(res)
}

# Returns Median (IQR) in rowvar X colvar dataframe + margins
mediqrby <- function(data, vvar, rowvar, colvar, digits = 0, colNamesMapping = NULL) {
  by.main <- by(data[[vvar]], 
                list(as.factor(data[[rowvar]]), as.factor(data[[colvar]])), 
                mediqr, 
                digits)
  array.main <- array(by.main, dim(by.main), dimnames(by.main))
  
  by.tot.col <- by(data[[vvar]], list(data[[rowvar]]), mediqr, digits)
  array.tot.col <-
    array(by.tot.col, dim(by.tot.col), dimnames(by.tot.col))
  
  by.tot.row <- by(data[[vvar]], list(data[[colvar]]), mediqr, digits)
  array.tot.row <-
    array(by.tot.row, dim(by.tot.row), dimnames(by.tot.row))
  
  grand.tot <- mediqr(data[[vvar]], digits)
  Total <- c(array.tot.row, grand.tot)
  temptab <- rbind(cbind(array.main, array.tot.col), Total)
  temptab <- as.data.table(cbind(row.names(temptab), temptab))
  setnames(temptab, 
           old = c(1, ncol(temptab)), 
           new = c(rowvar, "Overall"))
  if (!is.null(colNamesMapping)) {
    colNamesMapping <- colNamesMapping[names(colNamesMapping) %in% colnames(temptab)]
    setnames(temptab, 
             old = names(colNamesMapping), 
             new = colNamesMapping)  
  }  
  
  return(temptab)
}

# A function to return formatted 2-way tables of counts (%) and totals
ftab <- function(data,
                 x,
                 y,
                 digits = 1,
                 colNamesMapping = NULL,
                 row = TRUE) {
  freqs <- table(data[, c(x, y), with = FALSE])
  freqs <- rbind(freqs, Total = colSums(freqs))
  rfreqs <- prop.table(freqs, 1 * row + 2 * !row)
  ftable <- data.table(rownames(freqs))
  setnames(ftable, x)
  ftable <-
    cbind(ftable,
          matrix(
            paste0(freqs, " (", round(rfreqs * 100, digits), ")"),
            nrow = nrow(freqs),
            ncol = ncol(freqs),
            byrow = FALSE
          ),
          rowSums(freqs))
  setnames(ftable, 
           old = seq_len(ncol(ftable))[-1], 
           new = c(colnames(freqs), "Total"))
  if (!is.null(colNamesMapping)) {
    colNamesMapping <- colNamesMapping[names(colNamesMapping) %in% colnames(ftable)]
    setnames(ftable, 
             names(colNamesMapping), 
             colNamesMapping)  
  }
  return(ftable)
}

# A function to return formatted 2-way tables after MI; 
# 'data' already contains counts from prediction after MI
ftab_mi <- function(data, digits = 1, row = TRUE, colNamesMapping = NULL) {
  freqs <- as.matrix(data[, -1])
  freqs <- rbind(freqs, Total = colSums(freqs))
  rfreqs <- prop.table(as.table(freqs), 1 * row + 2 * !row)
  ftable <- rbind(data[, 1], data.table("Total"), use.names = FALSE)
  ftable <-
    cbind(ftable,
          matrix(
            paste0(round(freqs, digits = 0), " (", round(rfreqs * 100, digits), ")"),
            nrow = nrow(freqs),
            ncol = ncol(freqs),
            byrow = FALSE
          ),
          rowSums(freqs))
  setnames(ftable, 
           old = seq_len(ncol(ftable))[-1], 
           new = c(colnames(freqs), "Total"))
  if (!is.null(colNamesMapping)) {
    colNamesMapping <- colNamesMapping[names(colNamesMapping) %in% colnames(ftable)]
    setnames(ftable, 
             names(colNamesMapping), 
             colNamesMapping)  
  }  
  return(ftable)
}

# Extract var-cov matrix from quantreg model
cov.rq <- function(rqmodel) {
  return(diag(summary(rqmodel, covariance = TRUE)$cov))
}

# Returns list: 
# [[1]] - numeric values of median and q1, q3 for dateofdiagnosis and byvar (e.g. gender, 
#         transmission) - longformat
# [[2]] - strings of median (iqr) for dateofdiagnosis and byvar (e.g. gender, transmission) - wide 
#         format
mimediqrcd4 <- function(vvar, data, byvar, digits = 0, colNamesMapping = NULL) {
  data <- copy(data)
  data[, ':='(
    bv = as.factor(get(byvar)),
    vv = get(vvar)
  )]
  
  data.list = imputationList(split(data, 
                                   by = "Imputation"))
  for (i in seq(0.25, 0.75, by = 0.25)) {
    nam <- paste0("pred.", i)
    models <- with(data.list, 
                   rq(vv ~ bv * splines::ns(DY, df = nsdf), 
                      tau = i))
    vars <- MIextract(models, fun = cov.rq)
    betas <- MIextract(models, fun = coefficients)
    t <- MIcombine(betas, vars)
    X <- model.matrix(models[[1]]$formula)
    linpred <- (X %*% coef(t))^2
    pred <- cbind(data.list$imputations$`1`, 
                  linpred = as.vector(linpred))
    pred <- unique(pred[, c("DateOfDiagnosisYear", byvar, "linpred"), with = FALSE])
    setnames(pred, 3, nam)
    assign(nam, pred)
  }
  
  pred <- cbind(pred.0.25, pred.0.5[, 3], pred.0.75[, 3])
  pred[, ':='(
    mediqr = paste0(round(pred.0.5, digits), 
                    " (", round(pred.0.25, digits), ", ", round(pred.0.75, digits), ")")
  )]
  setorderv(pred, c("DateOfDiagnosisYear", byvar))
  wide <- dcast(pred, DateOfDiagnosisYear ~ get(byvar), value.var = "mediqr")
  
  pred[, mediqr := NULL]
  setnames(pred, 3:5, c("q1", "median", "q3"))
  
  if (!is.null(colNamesMapping)) {
    colNamesMapping <- colNamesMapping[names(colNamesMapping) %in% colnames(pred)]
    setnames(pred, 
             old = names(colNamesMapping), 
             new = colNamesMapping)  
  }
  return(list(pred, wide))
}

data <- copy(params[["AdjustedData"]]$Table)
cd4Present <- any(!is.na(data$SqCD4))
nsdf <- params[["AdjustedData"]]$Parameters$nsdf

if (!"Weight" %in% colnames(data)) {
  data[, Weight := 1]
}

# A. Make manipulations ---
data[Transmission %in% c(NA, "NA", ""), Transmission := "Missing"]

# Original data
data_orig <- subset(data, Imputation == 0)
data_orig[, ':='(
  CD4 = SqCD4^2,
  Transmission = factor(Transmission)
)]

# MI data
data_mi <- subset(data, Imputation != 0)
data_mi[, Transmission := factor(Transmission)]

# B. Collapsed data for Poisson regressions ---

# Unadjusted
temp_data_orig_gender <- data_orig[, .(Count = .N), by = .(DateOfDiagnosisYear, Gender)]
temp_data_orig_transmission <- data_orig[, .(Count = .N), by = .(DateOfDiagnosisYear, Transmission)]

# Adjusted
temp_data_mi_gender <- data_mi[, .(Count = sum(Weight, na.rm = TRUE)), by = .(Imputation, DateOfDiagnosisYear, Gender)]
temp_data_mi_transmission <- data_mi[, .(Count = sum(Weight, na.rm = TRUE)), by = .(Imputation, DateOfDiagnosisYear, Transmission)]

temp_data_mi_gender[, DY := DateOfDiagnosisYear - min(DateOfDiagnosisYear)]
temp_data_mi_transmission[, DY := DateOfDiagnosisYear - min(DateOfDiagnosisYear)]

if (cd4Present) {
  res.list.gender <- mimediqrcd4(vvar = "SqCD4", data = data_mi, byvar = "Gender")
  res.list.trans <- mimediqrcd4(vvar = "SqCD4", data = data_mi, byvar = "Transmission")

  maxOrigGender <- data_orig[, .(MaxMedian = median(CD4, na.rm = TRUE)), 
                             by = .(DateOfDiagnosisYear, Gender)][, max(MaxMedian, na.rm = TRUE)]
  maxOrigTrans <- data_orig[, .(MaxMedian = median(CD4, na.rm = TRUE)), 
                            by = .(DateOfDiagnosisYear, Transmission)][, max(MaxMedian, na.rm = TRUE)]
  maxMIGender <- res.list.gender[[1]][, max(q1, na.rm = TRUE)]
  maxMITrans <- res.list.trans[[1]][, max(q1, na.rm = TRUE)]

  cd4YLim <- GetNiceUpperLimit(max(maxOrigGender, maxOrigTrans, maxMIGender, maxMITrans))
}
```

# Unadjusted data

----------------------------------------------------------------------------------------------

The following tables and graphs are based on the original (unadjusted) data.
Table 1 and Figure 1 show number of diagnoses per year stratified by gender. Similarly, Table 3 and 
Figure 3 show number of diagnoses per year stratified by transmission category. Subjects with 
missing information on transmission category are shown as a separate group (labelled Missing).

```{r eval = cd4Present, include = cd4Present}
cat("Tables 2 and 4 (and corresponding Figures 2 and 4) show median CD4 cell counts at diagnosis 
     per year stratified by gender and transmission category, respectively. As the data are unadjusted 
     missing CD4 cell counts have been excluded from the calculations.")
```

**Table 1. Number of diagnoses per year by gender and overall**  
```{r}
table1 <- ftab(data = data_orig, x = "DateOfDiagnosisYear", y = "Gender", digits = 2, 
               colNamesMapping = c(DateOfDiagnosisYear = "Year of diagnosis", 
                                   F = "Female [N (%)]", 
                                   M = "Male [N (%)]",
                                   Total = "Total [N]"))
knitr::kable(table1, align = rep("r", ncol(table1)))
```

**Figure 1. Number of diagnoses per year by gender**  
```{r}
ggplot(temp_data_orig_gender) + 
  aes(x = DateOfDiagnosisYear, y = Count, color = Gender) +
  geom_point() +
  geom_line() +
  labs(x = "Year", y = "Number of diagnoses")  +
  scale_color_discrete(name = "Gender", labels = c("Female", "Male"))
```



```{r eval = cd4Present, include = cd4Present}
table2 <- mediqrby(data = data_orig, "CD4", "DateOfDiagnosisYear", "Gender", 
                   colNamesMapping = c(DateOfDiagnosisYear = "Year of diagnosis",
                                       M = "Male",
                                       F = "Female"))
cat("**Table 2. Median (IQR) CD4 cell count (cells/microL) by gender**  ")
knitr::kable(table2, row.names = FALSE, align = rep("r", ncol(table2)))

cat("**Figure 2. Median CD4 cell count (cells/microL) by gender**<br />")
ggplot(data_orig) +
  aes(x = DateOfDiagnosisYear, y = CD4, color = Gender) + 
  stat_summary(fun.y = "median", na.rm = TRUE, geom = "line") + 
  stat_summary(fun.y = "median", na.rm = TRUE, geom = "point") + 
  labs(x = "Year", y = "Median CD4 cell count (cells/microL)") +
  scale_color_discrete(name = "Gender", labels = c("Female", "Male")) + 
  coord_cartesian(ylim = c(0, cd4YLim))
```

----------------------------------------------------------------------------------------------------
  
**Table 3. Number of diagnoses per year by transmission category and overall**  
```{r}
table3 <- ftab(data_orig, x = "DateOfDiagnosisYear", y = "Transmission", digits = 2, 
               colNamesMapping = c(DateOfDiagnosisYear = "Year of diagnosis",
                                   HETERO = "Hetero [N (%)]",
                                   IDU = "IDU [N (%)]",
                                   MSM = "MSM [N (%)]",
                                   Missing = "Missing [N (%)]",
                                   Total = "Total [N]"))
knitr::kable(table3, row.names = FALSE, align = rep("r", ncol(table3)))
```

**Figure 3. Number of diagnoses per year by transmission category**  
```{r}
ggplot(temp_data_orig_transmission) + 
  aes(x = DateOfDiagnosisYear, y = Count, color = Transmission) +
  geom_point() +
  geom_line() +
  labs(x = "Year", y = "Number of diagnoses") +
  scale_color_discrete(name = "Transmission \ncategory", labels = c("Hetero", "IDU","MSM", "Missing"))
```

```{r eval = cd4Present, include = cd4Present}
table4 <- mediqrby(data_orig, "CD4", "DateOfDiagnosisYear", "Transmission", 
                   colNamesMapping = c(DateOfDiagnosisYear = "Year of diagnosis",
                                       HETERO = "Hetero"))
cat("**Table 4. Median (IQR) CD4 cell count (cells/microL) by transmission**")
knitr::kable(table4, row.names = FALSE, align = rep("r", ncol(table4)))

cat("**Figure 4. Median CD4 cell count (cells/microL) by transmission***<br />")
ggplot(data_orig) +
  aes(x = DateOfDiagnosisYear, y = CD4, color = Transmission) + 
  stat_summary(fun.y = "median", na.rm = TRUE, geom = "line") + 
  stat_summary(fun.y = "median", na.rm = TRUE, geom = "point") + 
  labs(x = "Year", y = "Median CD4 cell count (cells/microL)")  +
  scale_color_discrete(name = "Transmission\ncategory", 
                       labels = c("Hetero", "IDU","MSM", "Missing")) + 
  coord_cartesian(ylim = c(0, cd4YLim))
```

# Adjusted data

----------------------------------------------------------------------------------------------------
  
The following tables and graphs are on the adjusted for missingness (by Multiple Imputations) data.
Table 5 and Figure 5 show number of diagnoses per year stratified by transmission. Data stratified 
by gender are not shown since there were no missing data on gender thus one could refer to Table 1 
and Figure 1 of the unadjusted data.

```{r eval = cd4Present, include = cd4Present}
cat("Tables 6 and 7 (and corresponding Figures 6 and 7) show median CD4 cell counts at diagnosis per 
     year stratified by gender and transmission category, respectively. Calculations use imputed 
     values of transmission category and CD4 counts in cases where they were missing in the original 
     data. Year of diagnosis entered through splines in the models used to produce the results of 
     Tables/Figures 6 and 7.")
```

**Table 5. Number of diagnoses per year by transmission category and overall**  
```{r}
# mitools doesn't like factors with 0 frequency levels
temp_data_mi_transmission[, Transmission := droplevels(Transmission)]

# Fit saturated Poisson model to MI data
data.list <- imputationList(split(temp_data_mi_transmission, by = "Imputation"))

# Main model
models <- with(data.list,
               glm(Count ~ as.factor(Transmission) * splines::ns(DY, df = nsdf),
                   data = temp_data_mi_transmission,
                   family = poisson(link = log)))

# Extract betas and var  
vars <- MIextract(models, fun = vcov)
betas <- MIextract(models, fun = coefficients)
# Rubin's rules applied by  MIcombine
t <- MIcombine(betas, vars)
X <- model.matrix(models[[1]]$formula)

# Linear predictor exponentiated to get predicted counts
linpred <- exp(X %*% coef(t))
# Manipulation to end-up with a wide-format dataframe
pred <- cbind(data.list$imputations$`1`, linpred = as.vector(linpred))
pred <- pred[, .(DateOfDiagnosisYear, Transmission, linpred)]
wide <- dcast(pred, DateOfDiagnosisYear ~ Transmission, value.var = "linpred")

# ftab_mi will calculate row percentages and totals
table5 <- ftab_mi(wide, digits = 2, colNamesMapping = c(DateOfDiagnosisYear = "Year of diagnosis",
                                                        HETERO = "Hetero"))

# Show with kable
knitr::kable(table5, align = rep("r", ncol(table5)))
```

**Figure 5. Number of diagnoses per year by transmission category**  
```{r}
ggplot(pred) +
  aes(x = DateOfDiagnosisYear, y = linpred, color = Transmission) +
  geom_point() +
  geom_line() +
  labs(x = "Year", y = "Number of diagnoses") +
  scale_color_discrete(name = "Transmission \ncategory", labels = c("Hetero", "IDU","MSM"))
```

```{r eval = cd4Present, include = cd4Present}
table6 <- res.list.gender[[2]]
cat("**Table 6.  Median (IQR) CD4 cell count (cells/microL) by gender**")
knitr::kable(table6, row.names = FALSE, align = rep("r", ncol(table6)), 
             col.names = c("Year of diagnosis", "Female", "Male"))

cat("**Figure 6. Median CD4 cell count (cells/microL) by gender***<br />")
ggplot(res.list.gender[[1]]) +
  aes(x = DateOfDiagnosisYear, y = median, color = Gender) +
  geom_point() +
  geom_line() +
  labs(x = "Year", y = "Median CD4 cell count (cells/microL)") +
  scale_color_discrete(name = "Gender", labels = c("Female", "Male")) + 
  coord_cartesian(ylim = c(0, cd4YLim))

cat("*<br />**Table 7.  Median (IQR) CD4 cell count (cells/microL) by transmission**")
table7 <- res.list.trans[[2]]
knitr::kable(table7, row.names = FALSE, align = rep("r", ncol(table7)), 
             col.names = c("Year of diagnosis", "Hetero", "IDU","MSM"))

cat("**Figure 7. Median CD4 cell count (cells/microL) by transmission**<br />")
ggplot(res.list.trans[[1]]) +
  aes(x = DateOfDiagnosisYear, y = median, color = Transmission) +
  geom_point() +
  geom_line() +
  labs(x = "Year", y = "Median CD4 cell count (cells/microL)") +
  scale_color_discrete(name = "Transmission \ncategory", labels = c("Hetero", "IDU","MSM")) + 
  coord_cartesian(ylim = c(0, cd4YLim))
```
